### 2011-05-27 docs/architecture/architecture.tex
tweaks
add some notes on particles

A \bctower holds the information about what boundary conditions are
in effect for each variable in a MAESTRO simulation.  \MarginPar{better description?}

@@

>>>>

A \bctower\ holds the information about what boundary conditions are
in effect for each variable in a MAESTRO simulation.  \MarginPar{better description?}

@@

MAESTRO has support for Lagrangian particles that are passively
advected with the velocity field.  These are useful for diagnostics
and post-processing.  To use particles, particles must be seeded into
the domain by writing a problem-specific {\tt init\_particles.f90}
routine.  This routine is called at the start of the simulation.  The
{\tt init\_particles} routines add particles at specific locations by
calling the {\tt particle\_module}'s {\tt add} routine when a given
criteria is met by the fluid state.

When you run the code, particles are enabled by setting {\tt
  use\_particles = T}.  At the end of each timestep the locations of
all the particles are written out into a series of files called {\tt
  timestamp\_NN}, where {\tt NN} is the CPU number on which the
particle {\em currently} resides.  Particles are always kept on the
processor containing the state data corresponding to their present
location.  Several bits of associated data (density, temperature, and
mass fractions) are stored along with the particle ID and position.

Some simple python scripts allow for the plotting of the particle
positions.  For example, running {\tt test2} with particles enabled
will seed particles in the initial hotspot.  To plot the results,
first set your {\tt PYTHONPATH} environment variable to point to the
{\tt fParallel/data\_processing/python/} directory, for example:
\begin{verbatim}
export PYTHONPATH="/home/username/development/MAESTRO/fParallel/data_processing/python"
\end{verbatim}
This will allow python to see the {\tt parseparticles.py} routine.
For the {\tt test2} problem, the {\tt plotparticles.py} routine shows
how to plot the particle histories and make an animation of the
particles colored by the ash mass fraction.  This script is run as:
\begin{verbatim}
./plotparticles.py timestamp_*
\end{verbatim}

Note, these python routines require the NumPy and matplotlib packages.
On a Fedora Linux system, the necessary routines can be installed via:
\begin{verbatim}
yum install python-matplotlib lyx-fonts stix-fonts
\end{verbatim}
